UniScatter: Unifying\\Backscatter Communications, Symbiotic Radio and Reconfigurable Intelligent Surface

### 2022-08-17 main.tex
:pencil: Update information theory and input design

@@

				\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
				 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
				 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the coded backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K \times 1}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K \times 1}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is

@@

			Interestingly, the capacity-achieving decision design for \gls{dmtc} remains under-investigated, and some attempts were made for single source with binary inputs \cite{Qian2019b,Nguyen2021b}.

@@

		% In particular, we define a general bijective mapping from backscatter index tuples to ordered indexes $f : m_{\mathcal{K}} \to \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, and use both notation interchangably in the following context.
		% In particular, we define a general bijective mapping from backscatter index tuples to ordered indexes $\mathcal{M}^K \to \mathcal{L} \triangleq \{1,\ldots,L \triangleq M^K\}$, $m_{\mathcal{K}} \mapsto l$ and use both notation interchangably in the following context.

@@

		and backscatter channel coding can be performed on top of it.

@@

	\begin{subsection}{Achievable Rates}
		Denote the input probability of state $m_k$ of UniScatter node $k$ as $P_k(x_{m_k})$, and define the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{R}^{M \times 1}$. With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
		\begin{equation}
			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
			\label{eq:equivalent_distribution}
		\end{equation}
		% Denote the input probability distribution vector of tag $k$ as $\boldsymbol{p}_k \triangleq [P_k(x_1),\ldots,P_k(x_M)]^T \in \mathbb{R}^{M \times 1}$, where $P_k(x_{m_k})$ is the probability at state $m_k$.
		% Consider independent encoding at all tags such that the probability of input combination $x_{m_{\mathcal{K}}}$ is $P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k})$.
		% The backscatter information function of input combination $x_{m_{\mathcal{K}}}$ is defined as
		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$.
		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
		% Besides, the backscatter marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		Moreover, we can write the backscatter mutual information as
		\begin{equation}
			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}

		% Once the tag input combination is successfully decoded, the backscatter uncertainty can be eliminated and the equivalent channel for primary transmission can be updated by \eqref{eq:equivalent_channel}.

		% eliminate modulation uncertainty
		Once backscatter messages are successfully decoded, we can re-encode to determine $x_{\mathcal{K}}$ and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}. We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
		% Once backscatter symbols are successfully decoded, we can eliminate modulation uncertainty and retrieve equivalent primary channel by \eqref{eq:equivalent_channel}. We define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
		% \begin{equation}
		% 	I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) \triangleq \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right),
		% 	\label{eq:primary_information_function}
		% \end{equation}
		\begin{equation}
			I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
		% the primary marginal information function associated with letter $x_{m_k}$ of tag $k$ is
		\begin{equation}
			I_{\mathrm{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_marginal_information}
		\end{equation}
		and the primary ergodic mutual information as
		% and the primary (ergodic) mutual information is
		\begin{equation}
			% I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) \log \left(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\right).
			I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
			\label{eq:primary_mutual_information}
		\end{equation}

		% Moreover, with $\rho \in [0,1]$ being the relative priority of the primary link, we define corresponding weighted sum information function, marginal information, and mutual information respectively as
		Finally, with a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.

		% Therefore, the weighted sum information function, marginal information function, and mutual information of primary and backscatter links are respectively given by
		% \begin{align}
		% 	I(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{m_{\mathcal{K}}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
		% 	I_k(x_{m_k};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P},k}(x_{m_k};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
		% 	I(x_{\mathcal{K}};\hat{x}_{\mathcal{K}},\boldsymbol{y})
		% 	 & \triangleq \rho I_{\mathrm{P}}(x_{\mathcal{K}};\boldsymbol{y}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		% \end{align}
		% where $\rho \in [0,1]$ represents the priority of the primary link.
	\end{subsection}
	\label{se:uniscatter}
\end{section}

\begin{section}{Input Distribution, Active Beamforming, and Decision Threshold Design}
	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter network, we aim to maximize the weighted sum mutual information with respect to node input distributions $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming vector $\boldsymbol{w}$, and decision threshold vector $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}\in\mathbb{R}_+^{L+1}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		% \addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
		\addConstraint{\sum \nolimits_{m_k} P_k(x_{m_k})}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
		\addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k,m_k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
	\end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	\addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	% \begin{maxi!}
	% 	{\scriptstyle{\boldsymbol{p}_k \in \Delta^{M-1},\boldsymbol{t},\boldsymbol{w}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
	% 	% \addConstraint{\boldsymbol{p}_k}{\in \Delta^{M-1},}{\quad \forall k \in \mathcal{K}}{\label{co:sum_probability}}
	% 	% \addConstraint{P_k(x_{m_k})}{\ge 0,}{\quad \forall k \in \mathcal{K}, \ \forall m_k \in \mathcal{M}}{\label{co:nonnegative_probability}}
	% 	\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P.}{\label{co:transmit_power}}
	% \end{maxi!}
	Problem \eqref{op:weighted_sum_rate} is highly non-convex, and we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

	\begin{subsection}{Input Distribution}
		% For any fixed decision boundary $\boldsymbol{t}$ and transmit precoder $\boldsymbol{w}$, the equivalent \gls{dmtmac} can be formulated by \eqref{eq:dmtmac} and problem \eqref{op:weighted_sum_rate} boils down to
		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmtmac} by \eqref{eq:dmtmac} and simplify \eqref{op:weighted_sum_rate} to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$. Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
		\begin{remark}
			% As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are only necessary for such kind of problems and these solutions may end up being saddle points.
			As pointed out in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization in discrete memoryless \gls{mac}. Therefore, \gls{kkt} solutions may end up being saddle points of problem \eqref{op:input_distribution}.
		\end{remark}
		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions to their equivalent form for problem \eqref{op:input_distribution}, then propose an iterative method that guarantees input distribution satisfying above conditions on convergence.
		% Interestingly, the total-rate optimal input design for general discrete memoryless \gls{mac} remains an open problem, and we instead propose a \gls{kkt} solution to problem \eqref{op:input_distribution}.
		\begin{proposition}
			% The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k \in \mathcal{K}$ and $\forall m_k \in \mathcal{M}$,
			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			\label{pr:input_kkt_condition}
		\end{proposition}

@@

		For each node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} implies any state with potentially less marginal information should not be used.
		% We notice \eqref{eq:probable_states} means each probable state of each tag should produce the same marginal information (averaged over all states of other tags), while \eqref{eq:dropped_states} implies any state of any tag with potentially less marginal information than above should not be used.
		% Next, we generalize the Blahut-Arimoto algorithm \cite{Arimoto1972,Blahut1972a} and propose a numerical evaluation of \gls{kkt} points by limits of sequences.
		\begin{proposition}
			% The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
			The \gls{kkt} input probability of node $k$ of state $m_k$ is given by the converging point of the sequence
			% The \gls{kkt} solution of input probability of tag $k$ at state $m_k$ is given by the converging point of the sequence
			\begin{equation}
				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
				\label{eq:input_kkt_solution}
			\end{equation}
			% where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k \in \mathcal{K}$.
			where $r$ is the iteration index and $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$.
			\label{pr:input_kkt_solution}
		\end{proposition}
		\begin{proof}
			Please refer to Appendix \ref{ap:input_kkt_solution}.
			\label{pf:input_kkt_solution}
		\end{proof}

		At each iteration, the input distribution of node $k$ is evaluated over updated input distribution of node $1$ to $k-1$, together with previous input distribution of node $k+1$ to $K$. The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.

>>>>

		% \begin{subequations}
		% 	\label{eq:equivalent_channel}
		% 	\begin{align}
		% 		\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}})
		% 		 & \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k   \\
		% 		 & = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},
		% 	\end{align}
		% \end{subequations}
			\boldsymbol{h}_{\mathrm{E}}^H(x_{\mathcal{K}}) \triangleq \boldsymbol{h}_{\mathrm{D}}^H + \sum_{k \in \mathcal{K}} \alpha_k \boldsymbol{h}_{\mathrm{C},k}^H x_k = \boldsymbol{h}_{\mathrm{D}}^H + \boldsymbol{x}^H \mathrm{diag}(\boldsymbol{\alpha}) \boldsymbol{H}_{\mathrm{C}},

@@

		where $\alpha_k \in \mathbb{I}$ is the amplitude scattering ratio of UniScatter node $k$, $x_k \in \mathcal{X} \triangleq \{c_1,\ldots,c_M\}$ is the \emph{coded} backscatter symbol of node $k$, $\boldsymbol{\alpha} \triangleq [\alpha_1,\ldots,\alpha_K]^T \in \mathbb{I}^{K \times 1}$, $\boldsymbol{x} \triangleq [x_1,\ldots,x_K]^H \in \mathcal{X}^{K \times 1}$, and $\boldsymbol{H}_{\mathrm{C}} \triangleq [\boldsymbol{h}_{\mathrm{C},1},\ldots,\boldsymbol{h}_{\mathrm{C},K}]^H \in \mathbb{C}^{K \times Q}$. The signal received by the user at primary block $n \in \mathcal{N} \triangleq \{1,\ldots,N\}$ is

@@

			Interestingly, the capacity-achieving decision design for \gls{dmtc} remains under-investigated, and some attempts were made for a single source with binary inputs \cite{Qian2019b,Nguyen2021b}.

@@

@@

		then perform backscatter channel coding on top of it.

@@

	\begin{subsection}{Information Theory}
		Denote the input probability distribution vector of node $k$ as $\boldsymbol{p}_k \triangleq [P_k(c_1),\ldots,P_k(c_M)]^T \in \mathbb{I}^{M \times 1}$, and the probability of state $m_k$ as $P_k(x_{m_k})$.
		With independent encoding at all nodes, the probability of backscatter symbol tuple $x_{m_{\mathcal{K}}}$ is
		\begin{equation}
			P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) = \prod_{k \in \mathcal{K}} P_k(x_{m_k}).
			\label{eq:equivalent_distribution}
		\end{equation}

		Similar to \cite{Rezaeian2004}, we define the backscatter information function between input symbol tuple instance $x_{m_{\mathcal{K}}}$ and output symbol tuple variable $\hat{x}_{\mathcal{K}}$ as
		\begin{equation}
			I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K}}'} P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}}) \log \frac{P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})}{P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'})},
			\label{eq:backscatter_information_function}
		\end{equation}
		where $P_{\mathcal{K}}(\hat{x}_{m_{\mathcal{K}}'}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$ is the probability of channel output tuple $\hat{x}_{m_{\mathcal{K}}'}$.
		We also define the backscatter marginal information of letter $x_{m_k}$ of node $k$ as
		\begin{equation}
			I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),
			\label{eq:backscatter_marginal_information}
		\end{equation}
		where $P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) = \prod_{q \in \mathcal{K} \setminus \{k\}} P_{q}(x_{m_{q}})$.
		The backscatter mutual information can be written as
		\begin{equation}
			I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}).
			\label{eq:backscatter_mutual_information}
		\end{equation}
		Once backscatter messages of all nodes are successfully decoded, we can re-code for backscatter symbol tuple $x_{\mathcal{K}}$, recover their reflection patterns by \eqref{eq:backscatter_modulation}, and retrieve the equivalent primary channel by \eqref{eq:equivalent_channel}.
		Moreover, we define the primary information function conditioned on backscatter symbol tuple $x_{m_{\mathcal{K}}}$ as
		\begin{equation}
			I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) \triangleq \log \Bigl(1 + \frac{\lvert \boldsymbol{h}_{\mathrm{E}}^H(x_{m_{\mathcal{K}}}) \boldsymbol{w} \rvert^2}{\sigma_v^2}\Bigr),
			\label{eq:primary_information_function}
		\end{equation}
		the primary marginal information conditioned on letter $x_{m_k}$ of node $k$ as
		\begin{equation}
			I_{\mathrm{P},k}(s;y|x_{m_k}) \triangleq \sum_{m_{\mathcal{K} \setminus \{k\}}} P_{\mathcal{K} \setminus \{k\}}(x_{m_{\mathcal{K} \setminus \{k\}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}),
			\label{eq:primary_marginal_information}
		\end{equation}
		and the primary ergodic mutual information as
		\begin{equation}
			I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) = \sum_{m_{\mathcal{K}}} P_{\mathcal{K}}(x_{m_{\mathcal{K}}}) I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}).
			\label{eq:primary_mutual_information}
		\end{equation}

		With a slight abuse of notation, we define the corresponding weighted sum information function, marginal information, and mutual information respectively as
		\begin{align}
			I(x_{m_{\mathcal{K}}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{m_{\mathcal{K}}}) + (1 - \rho) I_{\mathrm{B}}(x_{m_{\mathcal{K}}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_information_function} \\
			I_k(x_{m_k})
			 & \triangleq \rho I_{\mathrm{P},k}(s;y|x_{m_k}) + (1 - \rho) I_{\mathrm{B},k}(x_{m_k};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_marginal_information}                     \\
			I(x_{\mathcal{K}})
			 & \triangleq \rho I_{\mathrm{P}}(s;y|x_{\mathcal{K}}) + (1 - \rho) I_{\mathrm{B}}(x_{\mathcal{K}};\hat{x}_{\mathcal{K}}),\label{eq:weighted_sum_mutual_information}
		\end{align}
		where $\rho \in \mathbb{I}$ is the relative priority of the primary link.
	\end{subsection}
	\label{se:uniscatter}
\end{section}

\begin{section}{Rate-Region Characterization}
	To characterize the achievable primary-total-backscatter rate region of the proposed UniScatter system, we aim to maximize the weighted sum mutual information with respect to input distribution $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, active beamforming $\boldsymbol{w}$, and decision thresholds $\boldsymbol{t}$ as
	\begin{maxi!}
		{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}},\boldsymbol{w},\boldsymbol{t}}}{I(x_{\mathcal{K}})}{\label{op:weighted_sum_rate}}{\label{ob:weighted_sum_rate}}
		\addConstraint{\boldsymbol{1}^T \boldsymbol{p}_k}{=1,}{\quad \forall k}{\label{co:sum_probability}}
		\addConstraint{\boldsymbol{p}_k}{\ge \boldsymbol{0},}{\quad \forall k}{\label{co:nonnegative_probability}}
		\addConstraint{\lVert \boldsymbol{w} \rVert^2}{\le P}{\label{co:transmit_power}}
		\addConstraint{t_{l-1}}{\le t_l,}{\quad \forall l.}{\label{co:decision_threshold}}
	\end{maxi!}
	Since problem \eqref{op:weighted_sum_rate} is highly non-convex, we propose a \gls{bcd} algorithm that iteratively updates $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{w}$ and $\boldsymbol{t}$ until convergence.

	\begin{subsection}{Input Distribution}
		For any given $\boldsymbol{w}$ and $\boldsymbol{t}$, we can construct the equivalent \gls{dmtmac} by \eqref{eq:dmtmac} and simplify \eqref{op:weighted_sum_rate} to
		\begin{maxi!}
			{\scriptstyle{\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}}}{I(x_{\mathcal{K}})}{\label{op:input_distribution}}{}
			\addConstraint{\eqref{co:sum_probability},\eqref{co:nonnegative_probability},}
		\end{maxi!}
		which involves the coupled term $\prod_{k \in \mathcal{K}} P_k(x_{m_k})$ and is non-convex when $K > 1$.
		Following \cite{Rezaeian2004}, we first recast \gls{kkt} conditions of problem \eqref{op:input_distribution} to their equivalent forms, then propose a numerical method that guarantees those conditions on convergence of sequences.
		% ? Next, we propose a numerical method that evaluate the \gls{kkt} input distribution by limit of sequences.
		\begin{remark}
			As demonstrated in \cite{Buhler2011}, \gls{kkt} conditions are generally necessary but insufficient for total rate maximization problems.
			Although \gls{kkt} solutions to problem \eqref{op:input_distribution} may end up being saddle points, we will later show by simulation their average performance can be reasonably close to optimal for a moderate $K$.
		\end{remark}
		\begin{proposition}
			The \gls{kkt} optimality conditions for problem \eqref{op:input_distribution} are equivalent to, $\forall k,m_k$,
			\begin{subequations}
				\label{eq:input_kkt_condition}
				\begin{alignat}{2}
					I_k^\star(x_{m_k}) & = I^\star(x_{\mathcal{K}}), \quad   &  & P_k^\star(x_{m_k}) > 0,\label{eq:probable_states} \\
					I_k^\star(x_{m_k}) & \le I^\star(x_{\mathcal{K}}), \quad &  & P_k^\star(x_{m_k}) = 0.\label{eq:dropped_states}
				\end{alignat}
			\end{subequations}
			\label{pr:input_kkt_condition}
		\end{proposition}

@@

		For each node, \eqref{eq:probable_states} suggests each probable state should produce the same marginal information (averaged over all states of other nodes), while \eqref{eq:dropped_states} suggests any state with potentially less marginal information should not be used.
		\begin{proposition}
			For any strictly positive initializer $\{\boldsymbol{p}_k^{(0)}\}_{k \in \mathcal{K}}$, the \gls{kkt} input probability of node $k$ at state $m_k$ is given by the converging point of the sequence
			\begin{equation}
				P_k^{(r+1)}(x_{m_k}) = \frac{P_k^{(r)}(x_{m_k}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k}) \Bigr)}{\sum_{m_k'} P_k^{(r)}(x_{m_k'}) \exp \Bigl( \frac{\rho}{1 - \rho} I_k^{(r)}(x_{m_k'}) \Bigr)},
				\label{eq:input_kkt_solution}
			\end{equation}
			where $r$ is the iteration index.
			\label{pr:input_kkt_solution}
		\end{proposition}
		\begin{proof}
			Please refer to Appendix \ref{ap:input_kkt_solution}.
			\label{pf:input_kkt_solution}
		\end{proof}

		For \eqref{eq:input_kkt_solution} at iteration $r+1$, the input distribution of node $k$ is updated over $\bigl\{\{\boldsymbol{p}_q^{(r+1)}\}_{q=1}^{k-1},\{\boldsymbol{p}_q^{(r)}\}_{q=k}^{K}\bigr\}$.
		The \gls{kkt} input distribution design is summarized in Algorithm \ref{al:input_distribution}.
